Global case

### 2025-05-06 lipschitz/Lipitschz.tex
update

	Recall the definition of Lipschitz continuity:
	 under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
	\end{align*} 
	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\epsilon$:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
		&  |\boldsymbol{x}-\boldsymbol{y}| < \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\epsilon)
	\end{align*} 
	In terms of the code, it is compute an optimization question respect to a certain number $\epsilon$:	\begin{align*}
			\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
	\end{align*} We can use this maximum value to estimate the Lipschitz constant.

	\section{pMILP and Local robustness}

@@

@@

	\section{Global robustness and Lipschitz constant}

	\subsubsection*{Constraints for $\gamma$}

>>>>

	Recall the definition of Lipschitz continuity:
	 under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
	\end{align*} 
	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\epsilon$:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
		&  |\boldsymbol{x}-\boldsymbol{y}| < \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\epsilon)
	\end{align*} 
	In terms of the code, it is compute an optimization question respect to a certain number $\epsilon$:	\begin{align}\label{global_robustness}
			\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
	\end{align} We can use this maximum value to estimate the Lipschitz constant.

	\section{Local robustness and pMILP}

@@

	First we introduce some concepts for local robustness question.

@@

	\section{Modeling for global robustness}

	We can modify the MILP model for local robustness to compute the question of global robustness \ref{global_robustness}.

	\subsubsection{Cloned model}

	The most straight way is to build two identical MILP models $M_1,M_2$ with completely disjoint variables (including inputs and outputs) with some extra constraints:

	\subsubsection{Simplified models}

	Constraints for $\gamma$
